Synthesizing Symmetric Lenses

### 2018-07-01 papers/SymmetricLenses/main.tex
eval efficiency

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 1 minute, and average the result over 5 runs. Figure~\ref{fig:times}
summarizes the results of these tests.
% end evaluation

>>>>

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{ Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional synthesis. }
  \label{fig:times}
\end{figure}

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 30 seconds, and average the result over 5 runs.
Figure~\ref{fig:times} summarizes the results of these tests. We find that our
algorithm is able to synthesize all of the benchmarks in our benchmark suite in
under 30 seconds.

The slowest completed benchmark for both the bijective and symmetric synthesis
algorithms is \lstinline{xml_to_augeas.boom}, a benchmark that converts
arbitrary XML up to depth 3 into a serialized version of the structured
dictionary representation used in Augeas.  This benchmark takes 18.9 seconds for
the symmetric synthesis algorithm to complete, and 9.3 seconds the bijective
synthesis algorithm to complete.
% end evaluation
